### 2020-08-14 code/survival/survfig.Rmd
Collect legends for cancer specific km plots

print(
((p1+mytheme)/((pstad[[1]]+mytheme)+(pgbm[[1]]+mytheme) +
(ppaad[[1]]+mytheme) + (thca[[1]] + mytheme)))/((pcanc+mytheme) + (pclass+mytheme))+plot_layout(design=mylayout) +plot_annotation(tag_levels = "A")
)

>>>>

kmlayout = "
AB
AB
AB
CD
CD
CD
EE
"
kmlegend <- theme(legend.direction = "horizontal")

print(
((p1+mytheme)/((pstad[[1]]+mytheme + kmlegend)+(pgbm[[1]]+mytheme + kmlegend) +
(ppaad[[1]]+mytheme + kmlegend) + (thca[[1]] + mytheme + kmlegend) + guide_area() + plot_layout(design = kmlayout, guides = "collect")))/((pcanc+mytheme) + (pclass+mytheme))+plot_layout(design=mylayout) +plot_annotation(tag_levels = "A")
)
